Self Regulation Ontology Retest Analyses

### 2018-05-03 code/SRO_Retest_Analyses.Rmd
wrapping up analyses using new release and draft

```{r}
tmp = tmp%>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "std_rt_error_icc", "avg_rt_icc", "std_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank())+
  scale_color_manual(values = cols,
                     breaks = c("Accuracy", "Missed percentage", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct",  "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)"))

@@

```{r}
rel_df[c(rel_df$dv %in% grep('threebytwo', rel_df$dv, value = TRUE)),]
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition") %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

@@

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))

@@

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition") %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000)%>%
  arrange(-median_icc, -median_spearman)

@@

```{r}
tmp = tmp%>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))

>>>>

```{r}
tmp = tmp%>%
  select(-median_spearman, -min_spearman, -max_spearman) %>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE))

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "std_rt_error_icc", "avg_rt_icc", "std_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_color_manual(values = cols,
                     breaks = c("Average RT error", "Accuracy", "SD RT error", "Missed percentage", "Average RT correct", "Cue switch cost Acc (100)", "SD RT correct", "Cue switch cost Acc (900)", "Cue switch cost RT (100)", "Task switch cost Acc (100)", "Task switch cost RT (100)", "Task switch cost Acc (900)", "Task switch cost RT (900)"))+
  ylim(-1,1)+
  guides(color = guide_legend(ncol=2, byrow=T))

@@

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

@@

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

@@

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != "other") %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

@@

```{r}
tmp = tmp%>%
  select(-min_spearman, -max_spearman,-median_spearman) %>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE),
         task_name = gsub("Survey", "", task_name))
